Subjective Experience of Demands and Resources across O*NET Job Elements

### 2023-12-30 Submission.Rmd
reworked intro to intro but nothing else

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes. However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands. We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure is frequently cited as a common demand; @demerouti2001job]. Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job]. Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical *a priori* assignment of a characteristic as objectively a "demand" or "resource". We explore this further below.

@@

As described above, job context and characteristics are assigned or appraised as demands or resources. Although much of our research on job demands in particular is based on *a priori* classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand). The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress]. Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).

>>>>

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes. However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job). Of particular importance here is that it is *the perception* of a characteristic or situation that determines which process an employee will experience despite the *a priori* objective assumption of a characteristic as objectively a "demand" or "resource". We explore this further below.

@@

Although much of our research on job demands in particular is based on *a priori* classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand). The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress]. Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).

### 2023-12-30 Submission.tex
reworked intro to intro but nothing else

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
\usepackage{dblfloatfix}

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes. However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands. We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001). One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}e.g., high work pressure is frequently cited as a common demand; Demerouti et al. (2001){]}. Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}. Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical \emph{a priori} assignment of a characteristic as objectively a ``demand'' or ``resource''. We explore this further below.

@@

As described above, job context and characteristics are assigned or appraised as demands or resources. Although much of our research on job demands in particular is based on \emph{a priori} classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand). The stress process speaks to how such individual difference in appraisal is possible. Lazarus and Folkman (1984) presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984). Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this task).

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
  pdflang={en-EN},
  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes. However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001). One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al. (2001)). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)). Of particular importance here is that it is \emph{the perception} of a characteristic or situation that determines which process an employee will experience despite the \emph{a priori} objective assumption of a characteristic as objectively a ``demand'' or ``resource''. We explore this further below.

@@

Although much of our research on job demands in particular is based on \emph{a priori} classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand). The stress process speaks to how such individual difference in appraisal is possible. Lazarus and Folkman (1984) presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984). Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor. Although not suggested by the names, primary and secondary appraisals can happen simultaneously. For instance, available resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this task).
